Supplementary Material for "Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-06-16 analysis/paper_draft4supp.Rmd
added Figure for 95% CI (ten strikes); changed Fig numbering.

---
title: Supplementary Material for "Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data"
date: "`r Sys.Date()`"
blinded: 0
authors:
- name: "[Sachin S. Pandya](https://orcid.org/0000-0001-7387-1307)"
  affiliation: University of Connecticut
  email: sachin.pandya@uconn.edu
- name: "Xiaomeng Li"
  affiliation: University of Connecticut
- name: "[Eric Barón](https://orcid.org/0000-0003-1934-1932)"
  affiliation: University of Connecticut
- name: "[Timothy E. Moore](https://orcid.org/0000-0002-9576-0517)"
  affiliation: University of Connecticut
output:
  bookdown::pdf_book: 
      base_format: rticles::asa_article
      citation_package: "default"
      keep_tex: TRUE
header-includes: 
  - \usepackage{amsmath}
  - \usepackage{subfig}
#fontsize: 12pt
bibliography: references.bib
biblio-style: agsm.bst

@@

Here, we extend section 3 of the paper by reporting our simulation results for 90% and 80% credible intervals.  We also extend the discussion in section 3.2 of the paper by discussing data collection and presenting additional illustrations of how a lawyer might use the prototype app.

# Bias Detection with 90% and 80% Credible Intervals

>>>>

---
title: Supplementary Material for "Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data"
date: "`r Sys.Date()`"
blinded: 0
authors:
- name: "[Sachin S. Pandya](https://orcid.org/0000-0001-7387-1307)"
  affiliation: University of Connecticut
  email: sachin.pandya@uconn.edu
- name: "Xiaomeng Li"
  affiliation: University of Connecticut
- name: "[Eric Barón](https://orcid.org/0000-0003-1934-1932)"
  affiliation: University of Connecticut
- name: "[Timothy E. Moore](https://orcid.org/0000-0002-9576-0517)"
  affiliation: University of Connecticut
output:
  bookdown::pdf_book: 
      base_format: rticles::asa_article
      citation_package: "default"
      keep_tex: TRUE
header-includes: 
  - \usepackage{amsmath}
  - \usepackage{subfig}
  - \newcommand{\beginsupplement}{
    \setcounter{table}{0}  
    \renewcommand{\thetable}{S\arabic{table}} 
    \setcounter{figure}{0} 
    \renewcommand{\thefigure}{S\arabic{figure}}
    }
#fontsize: 12pt
bibliography: references.bib
biblio-style: agsm.bst

@@

\beginsupplement

Here, we extend section 3 of the paper by reporting our simulation results for strike bias detection for the 95% credible interval (ten strikes per side) as well as such results for the 90% and 80% credible intervals for fifteen, ten, and six strikes per side.  We also extend the discussion in section 3.2 of the paper by discussing data collection and presenting additional illustrations of how a lawyer might use the prototype app.

# Additional Simulation Results for Strike Bias Detection

The number of strikes can affect bias detection as we define it.  The paper reports simulation results for bias detection for the 95% credible interval for trials with fifteen and six strikes per side.  Here, Figure \@ref(fig:figbd9510) depicts the simulation results for trials with ten strikes per side.

```{r figbd9510, out.width = "95%", fig.cap = "Bias detection rates (proportion of simulations where 0 is excluded from the 95 percent credible interval of bias parameter) for simulations based on 10 strikes.", fig.align='center'}

load_path <- here::here("figures","pp10_95CI.png")
knitr::include_graphics(load_path)
